{\Huge Supersymmetry} \\ \vspace{5mm} Lecture notes for FYS5190/FYS9190 Supersymmetry

### 2021-11-24 pheno.tex
Small number change

Supersymmetry may contribute to this process, {\it e.g.} with diagrams such as Fig.~\ref{btosdiags} b) where the  $m_{bs}^2\tilde{b}^*\tilde{s}$ mass term that changes a $\tilde b_1$ to a $\tilde s$ is a soft breaking off-diagonal term, often denoted $\delta_{23}$. The main MSSM contributions are expected to come from chargino--stop\footnote{We usually expect a higher generation off-diagonal terms to be larger due to RGE running controlled by Yukawa couplings.} and charged higgs--top loops, as shown in Figs.~\ref{btosdiags} c) and d), respectively. However,  there is little room for effects from superymmetry  since the current experimental world average is ${\rm Br}(B\to X_s\gamma)=(3.55\pm 0.26)\cdot 10^{-4}$ (PDG 2010). This means that either the charged Higgs is heavy enough and the stop-scharm soft mass term small enough, or that there are cancellations between the contributions.

>>>>

Supersymmetry may contribute to this process, {\it e.g.} with diagrams such as Fig.~\ref{btosdiags} b) where the  $m_{bs}^2\tilde{b}^*\tilde{s}$ mass term that changes a $\tilde b_1$ to a $\tilde s$ is a soft breaking off-diagonal term, often denoted $\delta_{23}$. The main MSSM contributions are expected to come from chargino--stop\footnote{We usually expect a higher generation off-diagonal terms to be larger due to RGE running controlled by Yukawa couplings.} and charged higgs--top loops, as shown in Figs.~\ref{btosdiags} c) and d), respectively. However,  there is little room for effects from superymmetry  since the current experimental world average is ${\rm Br}(B\to X_s\gamma)=(3.32\pm 0.15)\cdot 10^{-4}$ (PDG 2010). This means that either the charged Higgs is heavy enough and the stop-scharm soft mass term small enough, or that there are cancellations between the contributions.
